The Legacy of the European Post-Master in Urbanism at TU Delft: A Text Mining Approach

### 2025-02-03 analysis/paper/paper.qmd
Update abstract

---
title: "The Legacy of the European Post-Master in Urbanism at TU Delft: A Text Mining Approach"
author:
  - name: Claudiu Forgaci
    correspondence: "yes"
    email: c.forgaci@tudelft.nl
    orcid: 0000-0003-3218-5102
    affiliations: 
      - ref: tud
affiliations:
  - id: tud
    name: Delft University of Technology
    address: Julianalaan 134, 2628 BL, Delft, Zuid-Holland, The Netherlands
title-block-published: "Last updated"  
date: now
date-format: long
format:
  html: default
  # docx:
    # reference-doc: ../templates/template.docx
execute:
  echo: false
  warning: false
  message: false
  comment: "#>"
  fig-path: "../figures/"
  fig-dpi: 600
filters:
  - ../templates/scholarly-metadata.lua
  - ../templates/author-info-blocks.lua
  - ../templates/pagebreak.lua
bibliography: references.bib
csl: "../templates/journal-of-archaeological-science.csl" # Insert path for the bib-style
abstract: |
  This paper aims to describe the legacy of the European post-Master in Urbanism 
  (EMU) that ran between 2005 and 2021 at TU Delft. To that end, it reports on the
  analysis of the graduation theses produced over the duration of the program.
  The text mining approach allows for a close scrutiny of the latent thematic patterns, 
  and evolutions thereof, found in the full texts of the theses. Results reveal 5 topics
  that are to a large extent consistent with the set-up of the program in two thematic 
  semesters at TU Delft and three possible exchange semester locations, each characterised 
  by a specific approach. The paper discusses the relevance of the findings for the
  state of the profession and education in the field. Set up as a research
  compendium accompanied by a published FAIR dataset and an interactive dashboard, 
  the research is fully reproducible and enables further analysis. 
keywords: |
  urbanism; education; post-master; text mining; topic modeling
highlights: |
  These are the highlights. 
---

>>>>

---
title: "The Legacy of the European Post-Master in Urbanism at TU Delft: A Text Mining Approach"
author:
  - name: Claudiu Forgaci
    correspondence: "yes"
    email: c.forgaci@tudelft.nl
    orcid: 0000-0003-3218-5102
    affiliations: 
      - ref: tud
affiliations:
  - id: tud
    name: Delft University of Technology
    address: Julianalaan 134, 2628 BL, Delft, Zuid-Holland, The Netherlands
title-block-published: "Last updated"  
date: now
date-format: long
format:
  html: default
  # docx:
    # reference-doc: ../templates/template.docx
execute:
  echo: false
  warning: false
  message: false
  comment: "#>"
  fig-path: "../figures/"
  fig-dpi: 600
filters:
  - ../templates/scholarly-metadata.lua
  - ../templates/author-info-blocks.lua
  - ../templates/pagebreak.lua
bibliography: references.bib
csl: "../templates/journal-of-archaeological-science.csl" # Insert path for the bib-style
abstract: |
  After seventeen years of being part of the the European post-Master in 
  Urbanism (EMU), Delft Univerisity of Technology (TU Delft) left the program in
  2021. This paper aims to describe the legacy of TU Delft's contribution to the
  EMU and the profession. It reports on a topic model of graduation theses
  produced during the program. Results reveal topics that are consistent with
  the set-up of the program in two thematic semesters and three possible
  exchange semester locations. The paper discusses the relevance of the findings
  for the state of the profession and education in the field.
# TODO check sentences on results and discussion
# TODO JPER abstracts should generally be no longer than 125 words and have one sentence to
# answer each of the following questions:
# 1. What is the issue addressed and why is it important for planning theory or
# practice?
# 2. What gaps or misunderstandings in the literature does the research fill or correct?
# 3. How was the research conducted?
# 4. What are the research findings?
# 5. What are the conclusions for planning theory or practice and the implications for
# further research? 
keywords: |
  urbanism; education; post-master; text mining; topic modeling
highlights: |
  These are the highlights. 
---
